\begin{xltabular}{\linewidth}{lcrX}
	\toprule
	\scshape name & \scshape cookies & \faWeightHanging & \scshape story \\
	\midrule
	\endhead
	\bottomrule
	\endlastfoot

	\multicolumn{3}{l}{\itshape\bfseries Account\ldots} & \itshape\bfseries As a volunteer, I want\ldots \\*

	Signup & \cookiesvi & 2 & to create an account
	so that I can volunteer. \\*

	Login & \cookiesvi & 5 & to log in
	so that I can do stuff. \\*

	OAuth & \cookiesi & 10 & to log in with \textsc{Google} or \textsc{Facebook}
	so that I don't have to create yet another account for something. \\

	\midrule[0pt]
	\multicolumn{3}{l}{\itshape\bfseries Shifts\ldots} \\*

	Filter & \cookiesiv & 20 & to search and select shifts by time
	so that I can find shifts that fit my schedule. \\*

	Take & \cookiesvi & 2 & to sign up for shifts
	so that \textsc{LocalCinema} can stay open. \\*

	Select & \cookiesiii & 2 & to sign up for shifts in bulk
	so that I can get it over with quickly. \\*

	Receipt & \cookiesiv & 5 & to receive some kind of confirmation when I sign up for a shift
	so that I can be sure I have signed up for that shift. \\*

	Status & \cookiesvi & 1 & to see my shifts
	so that I can remember them. \\*

	Cancel & \cookiesvi & 1 & to cancel a shift
	so that I can tend to unexpected events. \\

	\midrule[0pt]
	\multicolumn{2}{l}{\itshape\bfseries Notify\ldots} \\*

	Help & \cookiesv & 10 & to be notified when my teams' upcoming shifts are unfilled
	so that I can potentially fill in in time. \\*

	Cancellation & \cookiesiv & 2 & to be notified when a shift is canceled
	so that I don't waste time. \\*

	Event & \cookiesi & 3 & to be notified of events
	so that I can join them. \\*

	Reminder & \cookiesv & 10 & to be notified when I have an upcoming shift
	so that I don't forget it. \\*

	Settings & \cookiesii & 2 & to edit my notification settings
	so that I am not spammed. \\

	\midrule[0pt]
	\multicolumn{2}{l}{\itshape\bfseries Team\ldots} \\*

	Join & \cookiesvi & 2 & to join a team
	so that I can do volunteer work I am interested in. \\*

	Super & \cookiesv & 1 & to see the current Super on duty
	so that I can contact them. \\*

	Members & \cookiesi & 1 & to see my teammates
	so that I can contact them. \\*

	Signups & \cookiesiv & 1 & to see who is signed up for a shift
	so that I can sign up with my buddies
	and harbor grudges against those that cancel right before a showing. \\

	\midrule[0pt]
	\multicolumn{2}{l}{\itshape\bfseries Profile\ldots} \\*

	Picture & \cookiesi & 2 & to upload a profile picture
	so that I can be stylish. \\*

	Stats & \cookiesv & 1 & to see my current rewards and statistics
	so that I can marvel at my philanthropy. \\*

	Rewards & \cookiesv & 5 & to cash in rewards
	so that I can enjoy them. \\

	\midrule[0.01pt]
	\multicolumn{3}{l}{\itshape\bfseries Announcements\ldots} & \itshape\bfseries As a Super, I want\ldots \\*

	News & \cookiesi & 10 & to pin information on a ``bulletin board''
	so that users can stay updated. \\

	\midrule[0pt]
	\multicolumn{3}{l}{\itshape\bfseries Notify\ldots} \\*

	Cancellation & \cookiesv & 20 & to be notified when a shift is canceled right before a showing
	so that I can fill in. \\

	\midrule[0pt]
	\multicolumn{3}{l}{\itshape\bfseries Moderation\ldots} \\*

	Ban & \cookiesiv & 5 & to ban a user
	so that they don't cause trouble. \\*

	Promote & \cookiesv & 5 & to promote users
	so that there can be more Supers. \\*

	Profiles & \cookiesi & 2 & users to have a profile picture
	so that I can easily distinguish between them. \\*

	Contact & \cookiesii & 5 & users to have an e-mail address or phone number
	so that I can contact them. \\

	\midrule[0.01pt]
	\multicolumn{3}{l}{\itshape\bfseries Support\ldots} & \itshape\bfseries As an IT administrator, I want\ldots \\*

	Reset & \cookiesv & 2 & to reset a user's email or password so that they can log in again. \\*

	Edit & \cookiesvi & 3 & to edit users' stats and rewards
	so that data can be migrated. \\*

	Logs & \cookiesiii & 5 & to read logs so that I can potentially fix operational errors. \\*

	Backups & \cookiesv & 10 & to backup and restore data
	so that \textsc{LocalCinema}'s operations can quickly recover. \\

	\midrule[0pt]
	\multicolumn{3}{l}{\itshape\bfseries Mitigation\ldots} \\*

	Emergency & \cookiesii & 10 & to turn off some features
	so that they cannot be abused. \\

	\midrule[0.01pt]
	\multicolumn{3}{l}{\itshape\bfseries Stability\ldots} \\*

	Uptime & \cookiesv & 5 & Have $99.5\%$ uptime
	so \textsc{LocalCinema} can stay operational. \\*

	\midrule[0pt]
	\multicolumn{3}{l}{\itshape\bfseries Experience\ldots} \\*

	Simple & \cookiesv & 10 & Have a simple UI/UX
	for the boomers.
\end{xltabular}
